% Abstract file structure example : 
% \abstitle{title here}
% \absauthors{names and superscripts for affiliations here}
% \absaddress{affiliations, starting each one with its superscripts, separate affiliations with a \break}
% \abstext{
% \index{author abbreviated name, to be placed in authors' index}
% \index{create an index entry for each author}
%  The abstract text
% }

%% Abstract title
\abstitle{Update upon important bat roosts in Mantua}

%% Author names
\absauthors{S. \textsc{Braghiroli}$^1$, M. \textsc{Spada}$^{2,5}$, D. \textsc{Scaravelli}$^3$, A. \textsc{Borghesan}$^4$, D. \textsc{Preatoni}$^2$ , A. \textsc{Martinoli}$^2$}

\absaddress{$^1$Via Germiniasi, Soave, Mantova\break
$^2$Unità di Analisi e Gestione delle Risorse Naturali – \textit{Guido Tosi Research Group}, Dipartimento di Scienze Teoriche e Applicate, Università degli Studi dell’Insubria, Via J. H. Dunant 3, I - 21100 Varese, Italy\break
$^3$Dipartimento di Scienze Mediche Veterinarie, Università degli Studi di Bologna, Via Tolara di sopra, 50 Bologna\break
$^4$Gruppo Speleologico Mantovano\break
$^5$Istituto Oikos srl, Via Crescenzago 1, Milano.}

%% Abstract text
\abstext{
%% Author names for index. State each author separately using \index{Doe J.}
\index{Braghiroli S.}
\index{Spada M.}
\index{Scaravelli D.}
\index{Borghesan A.}
\index{Preatoni D.}
\index{Martinoli A.}
%% The actual abstract text goes here
During the last five years, two important bat colonies have been discovered in Mantua: the first,
formed by bent-winged bats (\emph{Miniopterus schreibersii}, Kuhl, 1817), is located in the underground
of Corte Nuova, beside San Giorgio Castle into the Citadel of Mantua; the second, formed by
greater horseshoe bats (\emph{Rhinolophus ferrumequinum}, Schreber, 1774), is located inside the XIX 
century Stronghold of Pietole. Both colonies occupy historical buildings that face the complex of
lakes that surrounds Mantua; this wetland covers 2500 hectares and represents a precious
ecosystem in the agricultural system of the Po Plain.

The bent-winged bats colony was discovered in spring 2012 during an archaeological survey in the
undergrounds of Palazzo Ducale, led by the Mantuan Speleological Group. At that time, the colony
was formed by a thousand of individuals, but due to a series of catastrophic events that occurred in
the period of births (earthquake and flood), it was only in June 2015 that it could be identified as a
pre-reproductive aggregation formed by pregnant females and non reproductive individuals of both
sexes. For giving birth, females choose a still unidentified place, and the roost is occupied in
summer only by non reproductive individuals. This roost, partially flooded by the waters of the
Castle moat, is the most important known \emph{Miniopterus schreibersii}’s roost of Lombardy; is very
well preserved and inaccessible besides for research purposes.

The greater horseshoe bats colony was discovered during summer 2011, and the first surveys
confirmed the presence of nearly 35 reproductive females. The colony was present in the following
years but not in 2015. During this year, only three individuals at rest were found during a survey in
the month of April, while in June no animals were present. Pietole Stronghold is a huge fortress
formed by different rooms with peculiar physical conditions: they are dim lit, with fresh
temperatures and different degrees of humidity, thus forming suitable habitat for bats in different
periods of the year. This fortress is now managed by the municipality of Borgovirgilio, which is
starting a process of development, promotion and touristic use of the structure.
In May 2015, other strongholds in Mantua were visited (Fossamana and Lunetta fortress) but no bat
colonies were found.

Mantua is rich in historical buildings and environments suitable for bats that are still unexplored:
with its wetlands and woodlands related to the Mincio River, this territory could be an isle of
biodiversity in the middle of the Po Plain, but more efforts are needed to identify key habitat and
species and adopt sustainable management practices.
} %% remember to close the abstract text block brace!!